Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-22 analysis/paper/paper.Rmd
Remove reference to unused analysis

Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
This was downloaded, saved as an Open Document Spreadsheet (ODS) file for analysis.

Each article was rated on a 0 -- 3 scale for its data and code availability.
'Code availability' rated how easily and openly available the computational methods used in the article were.
Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
Lastly, the 'Data availability' evaluated how freely and openly available the data presented in the article were.
This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.

@@

A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and the agreed-upon criteria, so these scores were modified after discussion to match the ratings to the record of the software that was used in each respective paper.
For example, a paper was rated as having a `software_avail` rating of `3`, but the evaluator noted that Excel had been used; here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
In other cases, papers did not adequately describe all the software used, e.g., GenAlEx, an Excel add-on, was referred to but Excel was not mentioned in the text.
Here, Excel was added to the `software_used` column and the `software_avail` score was adjusted accordingly.

@@

The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020) using R 4.1.0 (R Core Team, 2021).

>>>>

The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
This was downloaded, saved as an Open Document Spreadsheet (ODS) file for analysis.

Each article was rated on a 0 -- 3 scale for its data and code availability.
'Code availability' rated how easily and openly available the computational methods used in the article were.
Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
Second, the 'Data availability' evaluated how freely and openly available the data presented in the article were.
This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.

@@

A custom function, `import_notes()`, was written to import the data and format the columns properly R [@RCT2022].
Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.

@@

The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
